Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-10-21 WSSSPE3/report/WSSSPE3_review.tex
Keynote: recap continued.

>>>>

In his keynote address, Turk recapped the course of developments of WSSSPE
workshops alongside with his career over the past few years. The first WSSSPE
workshop was at the Supercomputing Conference (SC13) in 2013, but he observed
that the notion of sustainable scientific software drew in an audience beyond
supercomputing. In the following year, WSSSPE1.1 at SciPy had speakers talking
about how software has been sustained inside the scientific Python community.
WSSSPE2 at SC14 had breakout group discussions coming up with actionable items,
and WSSSPE2.1 at SciPy~2015 was similar. Turk noted the different atmosphere and
perspectives of the surrounding large conferences, despite similar WSSSPE
participants. WSSSPE3 broke free of the Supercomputing Conference environment
this time, and in Turk's words, it spoke to the fact that scientific software
comes from many different types of inquiries, deployment, strategies for
maintenance, users, and ways of measuring the value of a piece of software.

%preconceptions
